% ABSTRACT

\begin{resumo}[ABSTRACT (OBRIGATÓRIO)]
\begin{Spacing}{1.5}

An essential competency in Computing education is the ability to understand, implement, and select suitable data structures for different problems. In this context, the advance of generative artificial intelligence tools, such as ChatGPT, has raised discussions about their possible effects on programming education. This work investigates the impact of ChatGPT usage on students' comprehension in the Data Structures and Algorithms course, focusing on Heap and Hash Table topics. The study adopts a crossover experimental design in which each group uses the tool in one topic and does not use it in the other. Comprehension was assessed through objective questionnaires applied at the end of each practical activity, without ChatGPT support. Twenty-five students were assigned to the groups, of whom 20 completed all experimental stages. Statistical analysis employed Shapiro--Wilk, Mann--Whitney U, Cliff's Delta, and paired Wilcoxon tests. No statistically significant difference in comprehension was identified between conditions with and without ChatGPT usage, and the effect size was classified as negligible ($\delta = -0.003$). These results converge with studies that also did not observe a significant impact of the tool on student performance in programming and data structures courses, although the participants' high prior familiarity with generative AI should be considered when interpreting the findings.

\end{Spacing}

\vspace{1cm}
\textbf{Keywords}: ChatGPT, generative artificial intelligence, data structures and algorithms, Heap, hash tables, comprehension.

\end{resumo}

% OBSERVAÇÕES:

% Escolha de 3 a 5 palavras ou termos que descrevam bem o seu trabalho .
% As palavras-chave são separadas por vírgula.

